Simulation Study: Varying Number of Tests

### 2018-10-31 datasets/simulations/simulations-informative-cosine.Rmd

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (cosine) function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with an informative and uninformative covariate. The informative covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (cosine) function of the covariate. The uninformative covariate is simply
uninformly sampled independently from the interval [0, 1]. The uninformative covariate is included
as a baseline to compare the informative covariate against. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

### 2018-10-31 datasets/simulations/simulations-uasettings-t.Rmd

---
title: "Simulation Study: Unimodal Settings (t test statistics)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-cubic.Rmd`. This set of simulations is similar to those
presented in `simulations-varyingeffectsize.Rmd`, however, t-distributed test
statistics are used.

>>>>

---
title: "Simulation Study: Unimodal Settings (t-11 test statistics)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. Both informative and uninformative covariates are included in the setting as described in
`simulations-informative-cubic.Rmd`. The effect sizes for non-null tests are
sampled from unimodal distributions composed of a mixture of normal distributions,
as described in the original adaptive shrinkage (ASH) manuscript (Stephens, 2016).

This set of simulations is similar to those presented in `simulations-uasettings.Rmd`.
However, t-distributed test statistics with 11 degrees of freedom are considered
rather than normally distributed test statistics.

### 2018-10-31 datasets/simulations/simulations-varyingntests.Rmd

In this set of simulations, we consider settings with varying number of hypothesis
tests. Since many newer FDR controlling approaches require fitting some model to
the independent covariates, they may be sensitive to lower number of tests. An
informative covariate is included in the setting as described in
`simulations-informative-sine.Rmd`.

>>>>

In this set of simulations, we consider settings with varying number of hypothesis
tests. Since many newer FDR controlling approaches require fitting some model to
the independent covariates, they may be sensitive to lower numbers of tests. Both
informative and uninformative covariates are included in these settings as described in
`simulations-informative-sine.Rmd`.
